Viscous Transport in Eroding Porous Media

### 2019-06-12 docs/transport/erosion_transport.tex
do the result section in transport paper

\begin{figure}[H]
\begin{center}
\includegraphics[width = 0.32\textwidth]{./figs/tracer_20b210_zoom}
\includegraphics[width = 0.32\textwidth]{./figs/tracer_20b240_zoom}
\includegraphics[width = 0.32\textwidth]{./figs/tracer_20b270_zoom}
\caption{\label{fig:Eroding20zoom}The zoom windows in the last three
  frames of Figure~\ref{fig:Eroding20tracer}. The trajectories of
  tracers around the bodies. Since we use a Barycentric quadrature rule
  and the fourth order Runge Kutta method, the tracers can be very close
  to but not penetrate the bodies.}
\end{center}
\end{figure}

@@

Since we use a Barycentric quadrature rule to approximate the velocity
of tracers and apply the fourth order Runge Kutta method to find the new
locations of tracers in each step, the tracers can be very close to but
not penetrate the bodies.  Those body-closed tracers are moving
perfectly so we are able to observe the details of the interaction of
bodies and fluid.  Although the direction of flow is from left to right,
the tracers will not only travel horizontally but also vertically.  In
the last three frames of Fig.~\ref{fig:Eroding20tracer}, some tracers
climb up from right to left around the body.  There are zoom windows of
the climbing tracers trajectories in Fig.~\ref{fig:Eroding20zoom} and
they are taken from the last three frames of
Fig.~\ref{fig:Eroding20tracer} with more tracers.  In
Fig.~\ref{fig:Eroding20zoom} the tracers around the center body first go
from the channel below the body, climb up to the left, then go to the
right and join another tracers in the channel above the body.

In Fig.~\ref{fig:Eroding20area} we
measure the area occupied by bodies 
during the eroding. In the beginning, 62.32\% of area of $[-1,1] \times
[-1,1]$ is occupied by 20 bodies. Then the eroding speed is increasing
when more and more bodies are vanished in the fluid and 
the maximum eroding speed happens when 7.57\% of area of $[-1,1] \times
[-1,1]$ is occupied by 8 bodies. After that the speed drops rapidly to 0 when
all the bodies are vanished completely.

@@

In Fig.~\ref{fig:Eroding20tort} we release 1000 tracers 
from the starting cross section x = -1 to 
the end cross section x = 1 and 
use the local tortuosity to analysis the effect
of the geometrical structure on fluid velocity field. In
Fig.~\ref{fig:Eroding20tort}(a) the graph represents the ratio of the
x-component velocity u(-1, y) to its maximum velocity $u_{max}=6.2281
\times 10^{-4}$ at equal spreading tracers on the starting cross section.
The velocity is continuous along the starting cross section and
acting as several Poiseuille flows. This velocity graph is different
from the one in~\cite{matyka2008tortuosity} since we choose our cross
section to be the beginning of the flow before the fluid touches any
body. In Fig.~\ref{fig:Eroding20tort}(b) we record the local tortuosity
$\tau(y)=\lambda(y)/d$
of the tracers at $y$ on the starting cross section x = -1 
where $d = 2$.
This graph is not continuous
and the jumps in $\tau$ mean that the initial neighbor tracers have been
seperated by the bodies.

In Fig.~\ref{fig:Eroding20tort}(c) we calculate the difference of 
$\tau$ at two neighboring tracers 
and draw the trajectories of neighboring tracers in 
Fig.~\ref{fig:Eroding20tort_traj}
if the difference of $\tau$ at the neighboring tracers is large. 
From Fig.~\ref{fig:Eroding20tort_traj},
 we are able to tell the neighboring trajectories will be very 
different if they are separated by bodies. In Fig.~\ref{fig:Eroding20tort_traj}
we collect the 10 largest difference of $\tau$ at the neighboring tracers and 
draw the pair of trajectories in the same color. For each pair of trajectories, 
they are splitted by the body at the left side of the body, then
one of them goes up and the other one goes down along the body 
until they rejoin with each other at the right side of body.  
Furthermore, the pair trajectories could be splitted by more than one body, 
for example in Fig.~\ref{fig:Eroding20tort_traj} the toppest red pair trajectories 
are splitted by three close bodies. 
}

@@

>>>>

@@

Since we use a Barycentric quadrature rule to approximate the velocity
of tracers and apply the fourth order Runge Kutta method to find the new
locations of tracers in each step, the tracers can be very close to but
not penetrate the bodies.  Those body-closed tracers are moving
perfectly so we are able to observe the details of the interaction of
bodies and fluid.  Although the direction of flow is from left to right,
the tracers will not only travel horizontally but also vertically.  In
the last three frames of Fig.~\ref{fig:Eroding20tracer}, some tracers
climb up from right to left around the body.  There are zoom windows of
the climbing tracers trajectories in Fig.~\ref{fig:Eroding20zoom} and
they are taken from the last three frames of
Fig.~\ref{fig:Eroding20tracer} with more tracers.  In
Fig.~\ref{fig:Eroding20zoom} the tracers around the center body first go
from the channel below the body, climb up to the left, then go to the
right and join another tracers in the channel above the body. 
}
\begin{figure}[H]
\begin{center}
\includegraphics[width = 0.32\textwidth]{./figs/tracer_20b210_zoom}
\includegraphics[width = 0.32\textwidth]{./figs/tracer_20b240_zoom}
\includegraphics[width = 0.32\textwidth]{./figs/tracer_20b270_zoom}
\caption{\label{fig:Eroding20zoom}The zoom windows in the last three
  frames of Figure~\ref{fig:Eroding20tracer}. The trajectories of
  tracers around the bodies. Since we use a Barycentric quadrature rule
  and the fourth order Runge Kutta method, the tracers can be very close
  to but not penetrate the bodies.}
\end{center}
\end{figure}
{\color{red}
In Fig.~\ref{fig:Eroding20area} we
measure the area occupied by bodies 
during the eroding. In the beginning, 62.32\% of area of $[-1,1] \times
[-1,1]$ is occupied by 20 bodies. Then the eroding speed is increasing
when more and more bodies are vanished in the fluid and 
the maximum eroding speed happens when 7.57\% of area of $[-1,1] \times
[-1,1]$ is occupied by 8 bodies. After that the speed drops rapidly to 0 when
all the bodies are vanished completely.

@@

In Fig.~\ref{fig:Eroding20tort} we release 1000 tracers 
from the starting cross section x = -1 to 
the end cross section x = 1 and 
use the local tortuosity to analysis the effect
of the geometrical structure on fluid velocity field. In
Fig.~\ref{fig:Eroding20tort}(a) the graph represents the ratio of the
x-component velocity u(-1, y) to its maximum velocity $u_{max}=6.2281
\times 10^{-4}$ at equal spreading tracers on the starting cross section.
The velocity is continuous along the starting cross section and
acting as several Poiseuille flows. This velocity graph is different
from the one in~\cite{matyka2008tortuosity} since we choose our cross
section to be the beginning of the flow before the fluid touches any
body. In Fig.~\ref{fig:Eroding20tort}(b) we record the local tortuosity
$\tau(y)=\lambda(y)/d$
of the tracers at $y$ on the starting cross section x = -1 
where $d = 2$.
This graph is not continuous
and the jumps in $\tau$ mean that the initial neighbor tracers have been
seperated by the bodies. 
}

@@

{\color{red}
In Fig.~\ref{fig:Eroding20tort}(c) we calculate the difference of 
$\tau$ at two neighboring tracers 
and draw the trajectories of neighboring tracers in 
Fig.~\ref{fig:Eroding20tort_traj}
if the difference of $\tau$ at the neighboring tracers is large. 
From Fig.~\ref{fig:Eroding20tort_traj},
 we are able to tell the neighboring trajectories will be very 
different if they are separated by bodies. In Fig.~\ref{fig:Eroding20tort_traj}
we collect the 10 largest difference of $\tau$ at the neighboring tracers and 
draw the pair of trajectories in the same color. For each pair of trajectories, 
they are splitted by the body at the left side of the body, then
one of them goes up and the other one goes down along the body 
until they rejoin with each other at the right side of body.  
Furthermore, the pair trajectories could be splitted by more than one body, 
for example in Fig.~\ref{fig:Eroding20tort_traj} the toppest red pair trajectories 
are splitted by three close bodies. 
}
